Towards Spherical Robots for Mobile Mapping in Human Made Environments\tnoteref{mytitlenote}

### 2021-08-30 Latex/sections/results.tex
added links to videos

\begin{figure*}
 	\centering
 	\begin{minipage}[c]{0.495\textwidth}
 		\centering
		\includegraphics[width=\textwidth]{./images/uncorr_bottom_pose}\\
		\includegraphics[width=\textwidth]{./images/uncorr_side_view}\\
  		\includegraphics[width=\textwidth]{./images/uncorr_hist}
  	\end{minipage}\hfill
  	\begin{minipage}[c]{0.495\textwidth}
  		\centering
		\includegraphics[width=\textwidth]{./images/corr_bottom_pose}\\
		\includegraphics[width=\textwidth]{./images/corr_side_view}\\
  		\includegraphics[width=\textwidth]{./images/corr_hist}
  	\end{minipage} 	
 	\caption{Evaluation of point distances before (left) and after (right) the plane-based registration on a simulated dataset. Lateral images always have the same orientation. A maximal distance of \SI{30}{m} is set, such that all points that display a higher distance value are excluded from the analysis. Both point-clouds were reduced before evaluating point-to-point distances to the ground-truth. Further, the color-space maps all values with a distance greater than \SI{1}{m} to the same color. The top two columns show a heat map of distances, while the bottom shows the corresponding histogram. The color mapping is equivalent in both. An animation of the matching process is given at \url{https://youtu.be/7igQdEeCsYk}.} 
 	\label{fig:simulatedEvaluation}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.495\textwidth]{./images/cylon_uncorr_corner}\hfill
	\includegraphics[width=0.495\textwidth]{./images/cylon_corr_corner}\\
	\includegraphics[width=0.495\textwidth]{./images/cylon_uncorr_top}\hfill
	\includegraphics[width=0.495\textwidth]{./images/cylon_corr_top}
	\caption{The point cloud acquired by the floating sphere before (left) and after (right) applying the plane based registration. View from the interior (top) and a birds-eye view (bottom). Parameters used for optimization: $\epsilon_H = 50$, $\epsilon_P = 200$, $\epsilon_\alpha = \frac{\pi}{4}$, $K = 20$ for AKNN, $d_{growth} = 50$, $N_{c_min} = 200$, $\alpha_0 = [0.01, 0.01, 0.01, 0, 0, 0]^\tau$, $i = 8$, $k = 100$. An animation of the registration process is given at \url{https://youtu.be/Qa2Qi8z0KEk} .}
	\label{fig:cylon-corrected}
\end{figure*}
After the registration, the walls of the room are significantly more prominent in the point cloud. 
In particular, the noise in the top left corner of the top view (cf. figure~\ref{fig:cylon-corrected}) has been visibly reduced.
Further, the deviation of points around the walls is notably smaller as the points are moved on the plane.

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.495\textwidth]{./images/jasper_uncorr_corner}\hfill
        \includegraphics[width=0.495\textwidth]{./images/jasper_corr_corner}\\
	\includegraphics[width=0.495\textwidth]{./images/jasper_uncorr_color}\hfill
	\includegraphics[width=0.495\textwidth]{./images/jasper_corr_color}\\
        \includegraphics[width=0.495\textwidth]{./images/jasper_uncorr_top}\hfill
        \includegraphics[width=0.495\textwidth]{./images/jasper_corr_top}
        \caption{The point cloud acquired by the rolling sphere before (left) and after (right) applying the plane based registration. View from the interior (top) and a birds-eye view (bottom). Parameters used for optimization: $\epsilon_H = 200$, $\epsilon_P = 300$, $\epsilon_\alpha = \frac{\pi}{4}$, $K = 200$ for AKNN, $d_{growth} = 50$, $N_{c_min} = 800$, $\alpha_0 = [0.001, 0.001, 0.001, 1, 0, 1]^\tau$, $i = 1500$, $k = 1$. An animation of the registration process is given at \url{https://youtu.be/2J8y7MN10JM}.}
        \label{fig:jasperhome}
\end{figure*}
After the registration, the walls of the environment are no longer ambiguous, since all the subsequent scans are matched with the initial plane representation.
When considering the resulting path, it looks distorted.
This is because for some scans, especially empty ones where the sensor points to the ground, no planar features got matched with the global plane model, thus their pose is not optimized.
Improving the path quality is an objective for future works.

>>>>

\begin{figure*}
 	\centering
 	\begin{minipage}[c]{0.495\textwidth}
 		\centering
		\includegraphics[width=\textwidth]{./images/uncorr_bottom_pose}\\
		\includegraphics[width=\textwidth]{./images/uncorr_side_view}\\
  		\includegraphics[width=\textwidth]{./images/uncorr_hist}
  	\end{minipage}\hfill
  	\begin{minipage}[c]{0.495\textwidth}
  		\centering
		\includegraphics[width=\textwidth]{./images/corr_bottom_pose}\\
		\includegraphics[width=\textwidth]{./images/corr_side_view}\\
  		\includegraphics[width=\textwidth]{./images/corr_hist}
  	\end{minipage} 	
 	\caption{Evaluation of point distances before (left) and after (right) the plane-based registration on a simulated dataset. Lateral images always have the same orientation. A maximal distance of \SI{30}{m} is set, such that all points that display a higher distance value are excluded from the analysis. Both point-clouds were reduced before evaluating point-to-point distances to the ground-truth. Further, the color-space maps all values with a distance greater than \SI{1}{m} to the same color. The top two columns show a heat map of distances, while the bottom shows the corresponding histogram. The color mapping is equivalent in both. An animation of the matching process is given at \url{https://youtu.be/hFx2uGkUdXw}.} 
 	\label{fig:simulatedEvaluation}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.495\textwidth]{./images/cylon_uncorr_corner}\hfill
	\includegraphics[width=0.495\textwidth]{./images/cylon_corr_corner}\\
	\includegraphics[width=0.495\textwidth]{./images/cylon_uncorr_top}\hfill
	\includegraphics[width=0.495\textwidth]{./images/cylon_corr_top}
	\caption{The point cloud acquired by the floating sphere before (left) and after (right) applying the plane based registration. View from the interior (top) and a birds-eye view (bottom). Parameters used for optimization: $\epsilon_H = 50$, $\epsilon_P = 200$, $\epsilon_\alpha = \frac{\pi}{4}$, $K = 20$ for AKNN, $d_{growth} = 50$, $N_{c_min} = 200$, $\alpha_0 = [0.01, 0.01, 0.01, 0, 0, 0]^\tau$, $i = 8$, $k = 100$. An animation of the registration process is given at \url{https://youtu.be//ov5Xjgyl9wA} .}
	\label{fig:cylon-corrected}
\end{figure*}
After the registration, the walls of the room are significantly more prominent in the point cloud. 
In particular, the noise in the top left corner of the top view (cf. figure~\ref{fig:cylon-corrected}) has been visibly reduced.
Further, the deviation of points around the walls is notably smaller as the points are moved on the plane.

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.495\textwidth]{./images/jasper_uncorr_corner}\hfill
        \includegraphics[width=0.495\textwidth]{./images/jasper_corr_corner}\\
	\includegraphics[width=0.495\textwidth]{./images/jasper_uncorr_color}\hfill
	\includegraphics[width=0.495\textwidth]{./images/jasper_corr_color}\\
        \includegraphics[width=0.495\textwidth]{./images/jasper_uncorr_top}\hfill
        \includegraphics[width=0.495\textwidth]{./images/jasper_corr_top}
        \caption{The point cloud acquired by the rolling sphere before (left) and after (right) applying the plane based registration. View from the interior (top) and a birds-eye view (bottom). Parameters used for optimization: $\epsilon_H = 200$, $\epsilon_P = 300$, $\epsilon_\alpha = \frac{\pi}{4}$, $K = 200$ for AKNN, $d_{growth} = 50$, $N_{c_min} = 800$, $\alpha_0 = [0.001, 0.001, 0.001, 1, 0, 1]^\tau$, $i = 1500$, $k = 1$. An animation of the registration process is given at \url{https://youtu.be/Mkil0vLk8f8}.}
        \label{fig:jasperhome}
\end{figure*}
After the registration, the walls of the environment are no longer ambiguous, since all the subsequent scans are matched with the initial plane representation.
When considering the resulting path, it looks distorted.
This is because for some scans, especially empty ones where the sensor points to the ground, no planar features got matched with the global plane model, thus their pose is not optimized.
Improving the path quality is an objective for future works.
